Recent demography drives changes in linked selection across the maize genome

### 2015-11-24 NatGen/manuscript.tex
updates

\section*{Results}

@@

\begin{figure}[!tb]
  \begin{center}
  \includegraphics[width=.45\textwidth] {FigsAndFiles/Pi_and_Tajima.png}
\end{center}
\caption{\textbf{A} and \textbf{B} Show pairwise diversity $\pi$, while \textbf{C} and \textbf{D} depict and Tajimas D in 1kb windows from genic and nongenic regions of maize (A,C) and teosinte (B,D). Shown in A and B are means $\pm$ one standard deviation.   \label{fig:diversity} }
\end{figure}

\begin{figure*}[!tb]
%\vspace*{.05in}
\centering
\includegraphics[width=.5\textwidth]{FigsAndFiles/DomesticationModel/domesticationModel.pdf}
\caption{Parameter estimates for a basic bottleneck model of maize domestication. See methods for details. \label{fig:bottleneck} }
\end{figure*}

@@

\section*{Discussion}

@@

\begin{acknowledgments}
We are indebted to Graham Coop and Simon Aeschbacher for their constructive input during this study. We thank Robert Bukowski and Qi Sun for providing early-access data from maize HapMap3. Funding was provided by NSF Plant Genome Research Project 1238014 and the USDA-Agricultural Research Service.
\end{acknowledgments}

>>>>

\section*{RESULTS}

@@

\begin{figure}[!tb]
  \begin{center}
  \includegraphics[width=.45\textwidth] {FigsAndFiles/Pi_and_Tajima.png}
\end{center}
\caption{\textbf{A} and \textbf{B} Show pairwise diversity $\pi$, while \textbf{C} and \textbf{D} depict and Tajimas D in 1kb windows from genic and nongenic regions of maize and teosinte. Shown in \textbf{A} and \textbf{B} are means $\pm$ one standard deviation.   \label{fig:diversity} }
\end{figure}

\begin{figure}[!tb]
%\vspace*{.05in}
\centering
\includegraphics[width=.5\textwidth]{FigsAndFiles/DomesticationModel/domesticationModel.pdf}
\caption{Parameter estimates for a basic bottleneck model of maize domestication. See methods for details. \label{fig:bottleneck} }
\end{figure}

@@

\section*{DISCUSSION}

@@

\section*{ACKNOWLEDGEMENTS}
We are indebted to Graham Coop and Simon Aeschbacher for their constructive input during this study. We thank Robert Bukowski and Qi Sun for providing early-access data from maize HapMap3. Funding was provided by NSF Plant Genome Research Project 1238014 and the USDA-Agricultural Research Service.

\section*{AUTHOR CONTRIBUTIONS}
TMB and JRI devised this study. TB, LW, and KC analyzed the data. AD performed early-stage simulations. MBH provided advice. TB, JRI, and MBH wrote the manuscript.

\section*{COMPETING INTERESTS STATEMENT}
The authors declare no competing financial interests.
